TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-11 paper/paper.tex
Added TCP congestion algorithm characteristics

		\subsubsection{Algorithm Characteristics}
		The BBR algorithm depends on the parameters BBR.BtlBw and BBR.RTprop. Those parameters are estimates defined by the BBR algorithm. \texttt{BtlBw} contains the bandwidth available to data transmissions ...
\\
\\

>>>>

		\subsubsection{Algorithm Characteristics}
		The BBR algorithm depends on parameters $BtlBw$ and $RT_{prop}$ \cite{bbr-congestion}. Those parameters are estimates defined by the BBR algorithm. $BtlBw$ specifies the bandwidth at the slowest link in each direction and $RT_{prop}$ is the round-trip propagation time. $RT_{prop} = RTT - queuing delay - processing delay$, which results in the minimum amount of time for round trip propagation in case there are no queueing or processing delays. Using those two parameters, the Bandwidth Delay Product (BDP) is calculated, which is the maximum possible amount of data being sent in a network: $BDP = BtlBw * RT_{prop}$. As long as the amount of data in transit is less than the $BDP$ and $BtlBw$, the delivery rate is increased. If the amount of data in transit is equal to $BtlBw$ the delivery rate can not go up anymore. The $RTT$ can never be lower than $RT_{prop}$... explain more on delay perhaps?.

		The CTCP algorithm is a combination of a loss-based and delay-based congestion protocol \cite{compound-tcp-congestion}. For the loss-based component, the variable conventional congestion window, $cwnd$, was introduced. For the delay-based component, the variable delay window, $dwnd$, was introduced. The TCP sending window is determined from: $win = min(cwnd + dwnd, awnd)$, where $awnd$ is the window advertised by the receiver. For $cwnd$ on the arrival of an ACK: $cwnd = cwnd + 1/win$. The $dwnd$ variable is initially set to zero and is only set when the congestion avoidance is active. $dwnd$ is calculated differently for several scenarios. If the network path is underutilized: $dwnd(t+1) = dwnd(t) + \alpha*dwnd(t)^{k} - 1$. When the network path is congested: $dwnd(t+1) = dwnd(t) - \eta*diff$. When packet loss occurs: $dwnd(t+1) = dwnd(t)(1-\beta) - cwnd/2$. $k$, $\alpha$, $\eta$ and $\beta$ are tunable parameters for optimization of the algorithm. $\eta$ defines the rapidness of reduction of the window when congestion is detected. $diff$ is calculated from the expected throughput and the actual throughput, which are again calculated from the window size and Round Trip Time (RTT).

		The DCTCP algorithm consists of three components \cite{dctcp-congestion-original}:
		\begin{enumerate}
			\item Simple Marking at the Switch. Based on the marking treshold $K$ a packet is marked with the CE flag. This only occurs when the queue occupancy is greater than K at arrival time. The marking treshold $K$ specifies the minimum value of queue occupancy.
			\item ECN-Echo at receiver. The receiver running the DCTCP algorithm ACKs every packet and sets the ECN-Echo flag only if the packet was marked with CE. The ECN-Echo flag is used to notify the sender of congestion in the network.
			\item Controller at the sender. The sender has an estimate of the fraction of packets that are marked with CE. This is based on the actual fraction of packets that were marked, the weight given to the new estimate compared to the past weight. This results in $\alpha$. $\alpha$ is used to indicate the congestion on a network with a maximum of value 1, indicating a congested network, and a minimum value of 0, indicating no congestion in the network. DCTCP cuts the window size using $\alpha$: $cwnd = cwnd * (1 - \alpha/2)$. This results in a low queue length, but ensuring high throughput.\\
		\end{enumerate}
